---
title: "Preliminary Descriptives & Plots of Starmaze Data"
author: "Patrizia Maier"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

### Task
Navigating a star-shaped maze environment ("Starmaze") with three goal locations.

### Time points of testing

Day 1

* Practise trials, including motor control (joystick) and task explanation.
* Navigation to and remembering the position of three goal locations. Baseline retrieval in egocentric (observer-dependent, i.e. from same starting point but without landmark cues) and allocentric (observer-independent, i.e. from new starting points) navigation condition.
  
Day 14

* Consolidated retrieval in egocentric and allocentric navigation condition.
* Non-navigational memory retrieval: Recognitve maze shape, recognize landmarks and goal objects, reconstruct location of landmarks and goal object.

### Sample
Cross-sectional comparison between

* young kids (6-7 yrs)
* older kids (9-10 yrs)
* young adults (18-35 yrs)
* older adults (68-75 yrs)


```{r setup, include = FALSE}
library(tidyverse)
library(arsenal)
```


```{r, load_data_script, include=FALSE, cache=FALSE}
file <- "../WP10_data/WP10_results/WP10_results_table.RData"
load(file)
rm(file)

knitr::read_chunk('Script_02_Table_Plot_Creator.R')
```


### Tables with descriptive values 
``` {r, table_settings, include=FALSE}
```

``` {r, table_learn, echo=FALSE, results="asis"}
```

``` {r, table_ego, echo=FALSE, results="asis"}
```

``` {r, table_allo, echo=FALSE, results="asis"}
```

